\plaintitle

### 2025-04-28 docs/style/article-body.tex
updates to article

>>>>

\subsection{\texorpdfstring{RESULTS }{RESULTS }}\label{results}

All iterations was tested on 6 different input datasets, with some results varying less than 0.1 microseconds. The results with such slight variations have been omitted from the table. All the tables shown below has been tested on the dataset `biased\_bits\_bad' which can be found as an appendix.

Due to compatibility issues, Pi Pico 2 was tested on different machine, creating further variation in the results -- about 1 microsecond.

\subsubsection{Iteration 1}\label{iteration-1}

The first iteration brought few surprises, as it ran quite well on Teensy. To our surprise, it executed well enough on Pi Pico 2 as well, albeit with \(~8\times\) slower execution speed.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Bit size}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Min (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Max (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Avg (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Min (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Max (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Avg (µs)}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
64 & 13 & 14 & 13.1564 & 103 & 117 & 106.3914 \\
512 & 788 & 791 & 788.3139 & 5296 & 5311 & 5302.4979 \\
1024 & 3124 & 3130 & 3124.0580 & 21108 & 21119 & 21111.2163 \\
\end{longtable}

\subsubsection{\texorpdfstring{Iteration 2 }{Iteration 2 }}\label{iteration-2}

Although the updated version included enhanced data structures, theoretical and practical analysis indicated that these modifications do not provide advantages for this project. Due to the small size of the input data (64, 512, 1024 bits) - using plain, contiguous memory layouts such as \texttt{std::vector\textless{}int\textgreater{}} proves to be very efficient in terms of access speed and memory usage. Current C++ compilers can effectively optimize these simple structures, often generating faster and more compact machine code than manually optimised alternatives. Introducing additional data structures or indirection would only add overhead without improving performance.

From an algorithmic perspective, Toeplitz extraction inherently requires a double summation loop, which leads to a time complexity of \(O(n^2)\) no matter the optimization applied internally. Thus, making attempts to change it would not result in lower asymptotic cost.

In summary, given the size and type of this system, a straightforward and minimal approach is not just adequate, but also recommended.

\subsubsection{Iteration 3}\label{iteration-3}

Coming soon!
